\LaTeXe\ guide for the Journal of Functional Programming

### 2019-05-02 papers/jfp/8-engineering.tex
Drop repeated text in S8.1

Our model assumes a world where the store is fully-defined, every \hs{k} is
associated with a \hs{v}, and every compute successfully completes returning a
valid value. In the real world, build systems frequently deal with errors, e.g.
``file not found'' or ``compilation failed''. We can model such failure
conditions by instantiating \hs{v} to either \hs{Maybe}~\hs{v} (for missing
values) or \hs{Either}~\hs{e}~\hs{v} (for exceptions of type \hs{e}). That can
model the errors inside the store and the \hs{Task}, but because our build
system models are polymorphic in \hs{v}, they cannot apply any special behaviour
for errors, e.g. aborting the build early. There are many other ways of
modelling errors, and in this section we show three simple examples.

As mentioned above, we can include failures into the type of values \hs{v}, for
example, to model a partial store we can use a simple like algebraic data type
isomorphic to \hs{Maybe}:

@@

\noindent
Here \hs{liftEither} wraps the result of the given
\hs{fetch}~\hs{::}~\hs{k}~\hs{->}~\hs{Either}~\hs{e}~\hs{v} into \hs{EitherT}
and then runs the task in the \hs{EitherT} monad
transformer~\cite{liang1995monad}.

>>>>

Our model assumes a world where the store is fully-defined, every \hs{k} is
associated with a \hs{v}, and every compute successfully completes returning a
valid value. In the real world, build systems frequently deal with errors, e.g.
``file not found'' or ``compilation failed''. There are many ways of modelling
errors, and in this section we give three simple examples.

% We can model such failure
% conditions by instantiating \hs{v} to either \hs{Maybe}~\hs{v} (for missing
% values) or \hs{Either}~\hs{e}~\hs{v} (for exceptions of type \hs{e}). That can
% model the errors inside the store and the \hs{Task}, but because our build
% system models are polymorphic in \hs{v}, they cannot apply any special behaviour
% for errors, e.g. aborting the build early.

One simple approach is to include failures into the type of values \hs{v}, for
example, to model a partial store we can use an algebraic data type isomorphic
to \hs{Maybe}:

@@

\noindent
Here \hs{liftEither} wraps the result of the given
\hs{fetch}~\hs{::}~\hs{k}~\hs{->}~\hs{Either}~\hs{e}~\hs{v} into \hs{ExceptT}
and then runs the task in the \hs{ExceptT} monad
transformer~\cite{liang1995monad}.
